

\subsection{Wednesday 8pm - 9:30}

\subsubsection{RHPS Meet and Great Spectacular}
\label{Wed-Meet-Greet}
{\small  Blue Room}

 We know some of you have heard the rumors.....
And we know that you've been waiting with antici.....pation....
And we're happy to say that (for once) the rumors are true so get ready to do the TIME WARP AGAIN!!!!
FPG Samhain 2015's Meet and Greet's theme is ROCKY HORROR PICTURE SHOW!
Complete with Shadow Cast, Audience Participation, Prop Bags and snacks!
Wednesday night at 9pm after Opening Ritual, don your best drag, your white undies, your sequins or come as you are and join us in what promises to be a bloody good time!
A note to parents, Rocky Horror is not a very kid friendly film, even more so with audience participation, so their attendance is at your own discretion. In order for our young pagans to enjoy an evening away from their parents we'll also be hosting a movie night and slumber party for the kids also starting at 9pm in the Arts and Crafts Hall. Please have your little ones in their PJs and have their pillow and sleeping bag or blankets with them and you can pick them up after the Meet and Greet. {\small (All ages)}

\subsubsection{Opening Ritual}
\label{Wed-OPENING}
{\small  Fire Circle}

 Please join the FPG staff as we introduce ourselves, give the famous ``YES'' speech, charge our Guardians, create Sacred Space, and let you in on some last-minute information. {\small (All ages)}

\subsubsection{Kids Movie Night "Double Feature"}
\label{Wed-kid-Meet}
{\small  Arts \& Crafts}

 8:45 pm-Midnight
Movies, popcorn, punch, and fun!  We have a wonderful night planned for our little witches and wizards at the Arts and Crafts Hall.  Dress them in their PJs and send along a blanket and pillow so they can get comfy and enjoy the evening while their folks attend the Opening Ritual and Rocky Horror Picture Show.  We will have staff from our Kids Realm supervising the evening while the kids watch their own "late night double-feature".  Potty-Trained to age 15 welcome! {\small (All ages)}