

\subsection{Thursday 9:30am - 10:30am}

\subsubsection{Healing Circle}
\label{Thu-Healing1}
{\small Grey Ghosthawk $\bullet$  Kids' Realm}

 Join us each morning for an Energy Healing Circle using many techniques including Usui Shiki Ryoho Reiki, Native American and Mexican Folk Medicine, and Peruvian Crystal Therapies. This is not a lecture-format workshop, but a hands-on healing session.  {\small (All ages; two hours)}

\subsubsection{Mindfulness Meditation}
\label{Thu-Fatolitis1}
{\small Christina Fatolitis $\bullet$  Freedom Circle}

 Come join Christina for morning meditation! Don't think you can meditate? If you can breathe, you can meditate. Beginners are always welcome, instructions will be joyfully given! Bring something you can sit on for 30 minutes, chairs are just fine, as long as you can sit comfortably. {\small (All ages)}

\subsection{Thursday 11am - 12:30}

\subsubsection{Goddess inspired tools and treats}
\label{Thu-Ivy1}
{\small IvyMoon $\bullet$  Arts \& Crafts}

 I will teach how to make wands and other crafts. The goal is to work in forgiveness to open closed spiritual doors. We will focus on ritual without the trimmings, envoking personal power to bring results. Personal readings may also be given.  {\small (All ages)}

\subsubsection{Solomonic Ritual - Invocation of the Elementals}
\label{Thu-Leitch1}
{\small Aaron Leitch $\bullet$  Morrigan's Arena}

 One of the fastest growing movements in the occult scene today is the revival of the Old Magick.  That is, magick as it was done before the rise of the 19th century magickal lodges (Golden Dawn, Thelema, etc) and modern Neopaganism and Wicca.  The Old Magick comes in many forms - from "fam-trad" witchcraft to the African Traditional Religions (Santeria, Palo, Voodoo), indigenous folk traditions (Hoodoo, Hexcraft, Stregheria) to native shamanism, and of course the medieval European spell books called "grimoires" that form the backbone of the Solomonic tradition (the Key of Solomon the King, Lemegeton, Heptameron, etc).

For the past one hundred years, the Solomonic grimoires have been conflated with the later lodge systems like the Golden Dawn, and are therefore often classified as "ceremonial magick."  However, as outlined in Aaron Leitch's "Secrets of the Magickal Grimoires", the magick of the grimoires is much more akin to sorcery, shamanism or folk magick.  If you are Pagan, you might be surprised by how familiar a Solomonic ritual will feel.

And now you have a rare opportunity to witness (or participate in) such a ritual for yourself!  FPG has invited grimoire masters Aaron Leitch and Carrie Mikell to perform a Solomonic Invocation of the Elementals.  We will be invoking the presence of the four classes of Elemental spirits (Salamanders, Undines, Sylphs and Gnomes) through the authority of the four "demon" Kings of the compass points.  They will be invited to partake of four Elemental offerings and in return will be asked to protect the festival grounds and guide all attendees in their own personal spiritual journeys.

While this will not be a full "evocation to visible appearance", the spirits very likely will make their presence known to those who are sensitive enough to see or hear them.  Therefore we will be inviting any and all skryers to attend and participate in the invocations.  Also, ALL who attend will be welcome to write their own private petitions to the spirits. {\small (All ages)}

\subsubsection{Flute Playing 101 Workshop}
\label{Thu-Mark1}
{\small Mark Wagenschnur $\bullet$  Vendors' Row}

 Learn the basics of playing Native American style flutes.  No prior musical experience is necessary.  Anyone can learn to play this entrancing instrument.  Mark provides all materials for the lesson, just come and learn!   You will be playing a song after just one lesson and you will be forever changed by the mystical powers of the flute.  Come let the meditative and soulful sounds take you on a journey.

Advanced flute playing lessons are also available. {\small (All ages)}

\subsection{Thursday 1:30pm - 3pm}

\subsubsection{Crafting the elements of dream workings}
\label{Thu-AMA2}
{\small Ann Marie Augustino $\bullet$  Blue Room}

 We will craft an oil and dream pillow to aid our dream work.  Following crafting these items we will charge them to work our magick. {\small (All ages)}

\subsubsection{Building the Sweat Lodge}
\label{Thu-Ghosthawk1}
{\small Grey Ghosthawk $\bullet$  Freedom Circle}

 Come help build the Lodge and learn the history and technique of how a Lodge is constructed.  Come prepared to work a little and have a little fun in the process. {\small (Ages 13 and up)}

\subsubsection{Celtic Games}
\label{Thu-Celts1}
{\small  Morrigan's Arena}

 Hear Ye! Hear Ye! Come one, come all to the Celtic Games! Show your strength \& stamina, and test your speed \& strategy in the Water Seige; and compete for honor \& fame in our traditional combat list!  The participant with the most points over the course of \textit{all} the games will be crowned FPG Grand Champion! 12 \& under must be accompanied by an adult.  Remember to bring a chair or blanket to sit on. Thurs: Early Sign-up {\small (All ages; see p.{celticgames})}

\subsection{Thursday 3:30pm - 5:30pm}

\subsubsection{DIVINATION AND MAGIC USING THE RUNES}
\label{Thu-Fitch4}
{\small Ed Fitch $\bullet$  Blue Room}

 Learn the secret magical methods of ancient Northern Europe, and how the Vikings could predict the future with their spiritual writing. Workshop: Practice these techniques! {\small (All ages)}

\subsubsection{Do Pagans Have Soul?}
\label{Thu-Mage1}
{\small Moonbeam Mage $\bullet$  Thunderdome}

 While as Pagans we honor Spirit and the spirits of all things, where do we stand concerning Soul? Do Pagans ponder the journey of their soul? Do we strive to live in a way that honors our Soul's journey? This workshop is intended to give each of us an opportunity to imagine, lay a foundation for, and clarify our understanding of "Soul" and what many call "the journey of the Soul." This will be an active, lively discussion where anyone may gain useful insight into the questions of Soul. It will also prepare participants to join the Evolutionary Astrology workshops with a clearer understanding of their own beliefs concerning Soul.  {\small (Ages 13 and up)}

\subsubsection{Honor in the Modern Day}
\label{Thu-Thor1}
{\small Thor $\bullet$  FSL \& StS}

 When classes in "Ethics" are needed to show people how to act or they are thought to lack "Morals" because their faith is different than others, is Honor, like Chivalry, already dead? Join Thor for a discussion on living an Honorable life in our modern era.  Please bring a chair or blanket. {\small (Ages 13 and up)}

\subsubsection{Rune Magic}
\label{Thu-Cannon1}
{\small Rev. Amber Cannon $\bullet$  Sanctuary}

 Runes can be used for a variety of magical purposes and combined to make amulets or talismans. In order to use them, you should have a knowledge of how they interact with each other. This will provide a refresher for people who work with them and discuss ways to include them in your practices. All your questions about runes can be answered.  {\small (Ages 13 and up)}

\subsubsection{Goddess Dolls}
\label{Thu-JoAnn1}
{\small JoAnn $\bullet$  Arts \& Crafts}

 We're going to take some felt and some beads and some thread and whatever else we can come up with and make our own personal representation of the goddess. Maybe we will even make some gods! Feel free to bring crystals or herbs along to personalize your dolls even further. Can't sew? A little glue goes a long way! I even have some plain muslin ones left from Beltane we can decorate! This workshop is more a of a free form funtime craft free-for-all! {\small (All ages)}

\subsubsection{Croquet}
\label{Thu-Croquet}
{\small Bruce-Robert Fenn Pocock $\bullet$  Ancestors' Glen}

 A completely arbitrary social event; a lawn billiards cocktail party for the whole family. Come join up for a team croquet game; just watch and meet folks, or take up a mallet and croquet your way across the bumpy lawn. Beginners are more than welcome! We'll also have Bocce. {\small (All ages)}

\subsubsection{Magic in the Color of Stones}
\label{Thu-magcolor}
{\small Mama Vic $\bullet$  Vendors' Row}

 We will talk about the properties of several stones and how they are affected by color.  This is an interactive workshop and each person will be asked to choose a stone they are attracted to or want to learn more about.  Each person attending will also get a stone to take with them. {\small (All ages)}

\subsection{Thursday 6:30pm -8:30 pm}

\subsubsection{The Center, The Spiral, The Boundary}
\label{Thu-Cypress1}
{\small Cypress $\bullet$  Blue Room}

 Different traditions structure sacred space in different ways. Do you declare sacred center, or cast a circle, or spiral out from ordinary reality? How does that sense of the sacred affect your way of working? Your sense of ordinary and non-ordinary reality? This class will include opportunities to explore various shapes and sizes of sacred space through both guided imagery and physical movement.  {\small (Ages 13 and up)}

\subsubsection{Master the Chakras for  Magickal Work}
\label{Thu-Shane1}
{\small Jamie Shane $\bullet$  Sanctuary}

 Beyond the basic understandings of these powerful centers lies a storehouse of useful energy. Through very basic physical techniques, we can call on them and tap into them to lend thrust to our workings. In this workshop you can expect to clear, gather and store energy for later use.  {\small (Ages 21 and up)}

\subsubsection{Women's Inipi Sweat Lodge}
\label{Thu-sweat-women}
{\small Grey Ghosthawk $\bullet$  Freedom Circle}

 Stone People Lodge, Purification Lodge, or inappropriately called a Sweat Lodge, is a sacred purification ceremony. This is similar to a sauna in outward appearance, but far more significant in meaning. It is a cleansing, not only of the body, but of the mind, heart, and spirit as well. This ceremony precedes almost all other Native American ceremonies. {\small (Ages 18 and up; two hours; Females only; see p.\pageref{sweatlodge}; see p.{celticgames})}

\subsubsection{Perceiving Ancestors Around Others:  A Medium Session Workshop}
\label{Thu-Ford2}
{\small Robin Murphy-Ford $\bullet$  Arts \& Crafts}

 This is a participation workshop looking past the Veil.  Samhain is the perfect time to see and ask the ancestors around others to communicate with us.  Special anointing oils and Gemstones will be supplied to assist your sight. Time permitting, Robin will convey messages from ancestors to attendees.  {\small (Ages 21 and up)}

\subsection{Thursday 7:30pm - 8:45pm}

\subsubsection{Main Ritual Practice}
\label{Thu-Prac1}
{\small  Main Ritual Circle}

 Closed to the Public {\small (All ages)}