

\subsubsection{Hands-On Healing by Holly Allender Kraig-Helton} { \small Holly is a certified massage therapist and Reiki Practitioner specializing in deep tissue massage and Thai massage. For just \$1 per minute, take time to relax and heal.  } 

\subsubsection{Melstroms Mess} { \small Headdresses, festival clothes, and accessories } 

\subsubsection{Minds Eye Graphics} { \small For all your fantasy t-shirt needs in sizes small - xxxl.We now have xxxxl and xxxxxl available by special order only. } 

\subsubsection{Mama Vic} { \small Crystals, minerals, gemstone jewelry, gift items, specialty items from all over the world.  We have been caretakers of the mineral kingdom for over 30 years.  We look forward to seeing you and helping you find the tools you need. } 

\subsubsection{The Rock Guy} { \small All natural gems and minerals from all over the world. Unique handmade gemstone jewelry and energy healing tools. Custom work also available. } 

\subsubsection{Nightbirds Journey} { \small Nightbird's Journey is a Pagan convenience store.  We carry everything from books and incense, herbs and jewelry.  Check out our "Bag Sale" for savings the entire weekend. } 

\subsubsection{Chainmaille} { \small I craft chain, link-by-link, day-by-day, looking for those wondrous objects that lie dormant in the chain and the scale and the art. } 

\subsubsection{Silve Fire Dreams} { \small I create using patterns and designs based on regional, ethnic influences and by adding unique twists with semi precious stones and Swarovski Crystal } 

\subsubsection{MW Flutes} { \small We offer a beautiful selection of hand crafted bamboo flutes and rattles, fishing flies and feather jewelry made by musician and craftsman, Mark Wagenschnur. } 

 \subsection{Other Vendors:} 

\indent 


 $ \bullet $ Piloshipher's stone 


 $ \bullet $ PJ 


 $ \bullet $ Morganna 


 $ \bullet $ Unleash the Goddess 


 $ \bullet $ Shiny Happy People Drum Tribe 


 $ \bullet $ Scholarship Fundraising 


 $ \bullet $ Guardian Fundraising 


 $ \bullet $ Mojo Chic 


 $ \bullet $ Ravens Moon Design 


 $ \bullet $ Mobile Massage 


 $ \bullet $ Spritual Pieces 


 $ \bullet $ You Rock Crystals 


 $ \bullet $ Lunsea Crafts 


 $ \bullet $ Spyder Flutes 

