

\subsection{Saturday 9:30am - 10:30am}

\subsubsection{Healing Circle}
\label{Sat-Healing3}
{\small Grey Ghosthawk $\bullet$  Kids' Realm}

 Join us each morning for an Energy Healing Circle using many techniques including Usui Shiki Ryoho Reiki, Native American and Mexican Folk Medicine, and Peruvian Crystal Therapies. This is not a lecture-format workshop, but a hands-on healing session.  {\small (All ages)}

\subsubsection{Mindfulness Meditation}
\label{Sat-Fatolitis3}
{\small Christina Fatolitis $\bullet$  Freedom Circle}

 Come join Christina for morning meditation! Don't think you can meditate? If you can breathe, you can meditate. Beginners are always welcome, instructions will be joyfully given! Bring something you can sit on for 30 minutes, chairs are just fine, as long as you can sit comfortably. {\small (All ages)}

\subsection{Saturday 11am - 12:30}

\subsubsection{Learning to Let Spirit Be Your Guide}
\label{Sat-DruAnn3}
{\small Dru Ann $\bullet$  Thunderdome}

 In 2007 Dru Ann started a journey of allowing Spirit to communicate with her and light her path. She developed the Spirit Guidance Oracle Cards to help her along the way. This workshop introduces you to ways to reach into your heart space for guidance as well as ways to use the cards or companion book to seek guidance.  The book and deck will be available for purchase at the workshop. {\small (All ages)}

\subsubsection{Talking with Wild plants, Trees and Fairies}
\label{Sat-Eagle1}
{\small Soaring Eagle $\bullet$  Isaac's Grove}

 Jaia Wise joins Soaring Eagle to present a workshop about deeply connecting with nature. Using voice, movement and meditation, we will tune in with wild plants and trees, and surrender to communing with their unique vibrations, residing divas and/or fairies. Perhaps they will have a message for us and/or reveal their unique forms and purposes. Participants are encouraged to express what they discover; talk, sing, dance, laugh, cry, sigh, or just listen. Please bring pen, pencils, paper and love. {\small (All ages)}

\subsubsection{VIKING SHAMANISM - FROM THE DENS OF THE WOLF-MOTHERS}
\label{Sat-Fitch1}
{\small Ed Fitch $\bullet$  Arts \& Crafts}

 Powerful, ancient legends of the North.  Viking magic and shamanism.  Portals into other dimensions.  Theories of face-changing and shape-changing.  Animal totems.  The Wolf mothers. The Elder races.  Shamanic spirituality.  Healing.  Introduction to rune divination and magic.  Viking ritual will be held at the conclusion of this evening. {\small (All ages)}

\subsubsection{Flute Playing 101 Workshop}
\label{Sat-Mark2}
{\small Mark Wagenschnur $\bullet$  Vendors' Row}

 Learn the basics of playing Native American style flutes.  No prior musical experience is necessary.  Anyone can learn to play this entrancing instrument.  Mark provides all materials for the lesson, just come and learn!   You will be playing a song after just one lesson and you will be forever changed by the mystical powers of the flute.  Come let the meditative and soulful sounds take you on a journey.

Advanced flute-playing lessons are also available. {\small (All ages)}

\subsection{Saturday 1:30pm - 3:30pm}

\subsubsection{Spiral Dance Concert}
\label{Sat-Concert2}
{\small Spiral Dance $\bullet$  Blue Room}

 Spiral Dance Concert {\small (All ages)}

\subsubsection{An Overview of the Tarot}
\label{Sat-Moura1}
{\small Ann Moura $\bullet$  Thunderdome}

 Ann Moura talks about the structure of the Tarot, what the cards can represent, how they can be related to the Witch's Craft, and offer tips on how to give meaningful readings for yourself and others. She will have her own Green Witch Tarot deck and book set, newly published by Llewellyn Worldwide, available for purchase at a special FPG 20% discount.  If time permits, a practice session will follow the talk and utilize 2 easy card spreads.  {\small (All ages)}

\subsubsection{Window wishing beads}
\label{Sat-Jordan1}
{\small Jenn $\bullet$  Arts \& Crafts}

 Window wishing beads for little ones to whatever age.  Stringing pretty shiny beads filling them with happy positive thoughts. We will make them to take home and enjoy watching the morning sun shine through. {\small (All ages)}

\subsubsection{Celtic Games}
\label{Sat-Celts3}
{\small  Morrigan's Arena}

 Hear Ye! Hear Ye! Come one, come all to the Celtic Games! Show your 
strength \& stamina, and test your speed \& strategy in the Water 
Seige; and compete for honor \& fame in our traditional combat list! 
 The participant with the most points over the course of \textit{all} 
the games will be crowned FPG Grand Champion! 12 \& under must be 
accompanied by an adult.  Remember to bring a chair or blanket to sit 
on. Sat: The List \& Champion Medal Ceremony  {\small (All ages; see p.{celticgames})}

\subsection{Saturday 4pm - 6pm}

\subsubsection{THE DARK GODDESS - COLORS OF THE SHADOWS}
\label{Sat-Fitch3}
{\small Ed Fitch $\bullet$  Thunderdome}

 The Third Aspect of the Lady.  Why study the Hecate aspect? What does it take to seek the Dark Path?  Legends.  Hazards and rewards.  Explore and understand the difference between "Dark" and "Evil".  The final reality at the end of all things.  She is powerful, so use care! Three aspects of the Dark Goddess.  What does She look like?  Study and meditation to learn more of the Dark Goddess. {\small (All ages)}

\subsubsection{Main Ritual Practice}
\label{Sat-Prac4}
{\small  Main Ritual Circle}

 Closed to the Public {\small (All ages)}

\subsubsection{Concepts of Deity}
\label{Sat-Cypress3}
{\small Cypress $\bullet$  Sanctuary}

 Among paganfolk, we find everything from hard polytheist/devotional polytheists to comfortably convinced atheists who like the community and values, in many permutations. So-- how does the way you experience the divine influence your experience and practice as a pagan? How can all these belief structures co-exist? How does the way you worship effect who you *are* as a spiritual being and a person? How do you decide who and how to worship? Can you be a "bad pagan"? This class is aimed at the relative newcomer, but I'm glad to have courteous input from other leaders/teachers about how they handle these questions. This is a class that Dancing Otters teaches fairly early on in our open class on Wicca, before the class on tending shrines and on patrons. It's mostly lecture and discussion. {\small (Ages 10 -- 21)}

\subsubsection{Satan, Demons and Hell - Why Are They in the Grimoires?}
\label{Sat-Leitch3}
{\small Aaron Leitch $\bullet$  Arts \& Crafts}

 For hundreds of years, the Western grimoires have been decried as evil texts full of appeals to Satanic entities, by which magicians sell their souls to the Great Enemy in return for temporary wealth or power here on Earth.  In recent decades, these texts have re-emerged into our culture - this time viewed in a more egalitarian light.  After all, there are grimoires full of angels and nature spirits who have no connection to the infernal realm.  There is really nothing "Satanic" about these books.  However...

While it is true most of this negative reputation is thanks to aggressive anti-occult propaganda from the Church, the grimoires themselves must bear some of the blame.  While there are plenty of angelic grimoires out there, it cannot be denied there are countless examples of grimoires that really do call upon Satan, Lucifer, Leviathan, Belial, Asmodeus, Baal, Lilith and hundreds (maybe thousands) of other denizens of hell.  This made it very easy for the Church to hold the texts up as proof that they are, in fact, devilish at heart.

Yet the European medieval/renaissance grimoires were primarily produced by devout Christians.  The image of the de-frocked priest performing Satanic Masses behind closed doors is not only the stuff of urban legend, but nothing remotely like it appears in the grimoires. Even the spells that call exclusively upon the rulers of Hell still make prayers and appeals to the Highest God to accomplish their goals.  So these people weren't Satan worshippers or even demonolaters - but that leaves us to question:  why in the world would devout Christian mystics even include Satan or anything hellish in their grimoires?  And, of course, what does that mean for those of us using the same texts today?

You might find the answer surprising - but more importantly you will see how the answer is vital to the Western mysteries, and to all of us attempting to revive the Old Magick in the modern world.  This lecture might just change how you think magick works! {\small (All ages)}

\subsubsection{Drum Flow (an ongoing experience)}
\label{Sat-Shiny1}
{\small Amber Forest and SHP drum tribe $\bullet$  Vendors' Row}

 At each festival we come together in the Drum Flow, an explosive drum meditation involving every member of Shiny Happy People Drum Tribe. Come create community through sound by slowly building a jam piece where everyone is involved, no matter your skill level. This free flow playshop allows for us to connect in the daytime hours and get ready for Saturday evening's festivities. So bring your smile and your creativity and let's have a good time! Some drums available first come first serve, and remember this is a sacred jam peice so if you show up late just jump right in and join us!!! {\small (Ages 10 and up)}

\subsection{Saturday 8pm - 9:30pm}

\subsubsection{Honoring the God and Celebrating 20 years of Florida Pagan Gathering}
\label{Sat-RITUAL}
{\small  Main Ritual Circle}

 At FPG Samhain Keepers of the Earth will lead a Rite to reconnect with our Honored Ancestors and Beloved Kin who now live beyond the veil. We shall reconnect with the people both familial and extraordinary who touched our lives, influencing who we have become, shaping our visions and our paths. We shall honor these Ancestors as our heroes. For what is a hero? To us a hero is someone whose impact on us cannot be measured.
 
There is a Yoruba proverb that says  ``We stand on the shoulders of our Ancestors.''  According to St. Augustine, the meaning of the Latin word for religion means  ``to reconnect.'' 
 
This ritual of reconnection shall utilize the power of a Druid ceremony, the essential magic of witchcraft, and the ancestral veneration of Asatru. Everyone who participates will have the opportunity to reconnect with their Heroes beyond the veil as we remember all Honored Ancestors with devotion and love. {\small (All ages)}